---
title: "M2_Hasib Noor Shahdin_2020_3_82_004"
author: "Hasib Noor Shadhin"
date: "12/11/2020"
output: word_document
---

```{r}
getwd()
setwd("G:/EWU/02 Semester 1/01 Analysis of Variance/R Classwork/Mid Term 2")
install.packages("outliers")
library(outliers)
install.packages("nonpar")
library(nonpar)
install.packages("GAD")
library(GAD)
```

```{r}
dat <- read.csv("mid2 data.csv")
str(dat)
```

# Cochran's Test
```{r}
cochrans.q(dat)
cochran.test(dat$Obs,c(6,6,6,6), inlying = TRUE)
```
Since p-value is less than 0.05, we can conclude that the equal variance assumption does not hold.

# Transformation
```{r}
sigmayi <- tapply(dat$Obs, dat$Method, sd)
sigmayi
mui <- tapply(dat$Obs, dat$Method, mean)
mui
logsigmayi <- log(sigmayi)
logsigmayi
logmui <- log(mui)
logmui
```

## Plotting logsigmayi against logmui and finding coefficeint
```{r}
plot(logsigmayi, logmui, type = "l")
lm(logsigmayi~logmui)
```
The coefficient of logmui is 0.9644. This value is approximately 1. So, we will have to use log transformation.

# Checking for equal variance in the transformed data
```{r}
dat1 <- read.csv("mid2 data.csv")
str(dat1)
```

## Using Bartlett's Test
```{r}
bartlett.test(Obs1~Method, data = dat1)
```
Since p-value is greater than 0.05 we cannot reject the null hypothesis. Thus, the variances are equal.

# Testing whether different methods differ
```{r}
anv1 <- aov(Obs1~Method, data = dat1)
summary(anv1)
```
Since p-value is less than 0.05, we can conclude that the mean of the different treatments are not equal.